### 2019-03-24 Sections/economics_of_the_quantum_internet.tex
Finished editing NL

\subsubsection{Adversarial enhancement}\index{Adversarial enhancement}

\famousquote{In savage countries they eat one another, in civilised ones they deceive one another; and that is what people call the way of the world!}{Arthur Schopenhauer}

\comment{To do}

\begin{itemize}
\item ...	
\end{itemize}

>>>>

\subsubsection{Strategic implications}\index{Strategy}

\famousquote{In savage countries they eat one another, in civilised ones they deceive one another; and that is what people call the way of the world!}{Arthur Schopenhauer}
\newline

It is clear that the \textsc{Unify} strategy, in which distinct quantum computing nodes are merged via the network into a larger distributed quantum computer, works to the (potentially exponential) benefit of all contributing parties. This distorts game-theoretic analysis of network participants compared to classical computing.

On one hand, the guaranteed mutual benefit of all players directly enhances their individual compute power. In a compute-centric world, where computation equates to productivity, this directly works in the self-interest of all.

However, taking a more strategic long-term perspective, despite self-enhancement, the associated enhancement of competitors may eventuate in outcomes that work against self-interest to a sufficient extent that it outweighs this benefit. Thus, cooperative enhancement, in an appropriate strategic context, could equally be tantamount to `adversarial enhancement'\index{Adversarial enhancement}, and be considered an overwhelming motivate to avoid cooperation with certain players.

Some non-technical discussion on the implications of these observations is presented in several of the essays in Part.~\ref{part:essays}.
